TKT RNAseq: PNP analysis

### 2025-01-28 TKT_RNAseq/R Code/TKTRNAseqPNPAssessment.Rmd
serpe data

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
mean.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)
cpmdata = G85R.cpm
groups = G85R.meta

@@

TerminalPoints = data.frame(enzyme = TerminalPoints$enzyme,
                            from = TerminalPoints$from,
                            to = TerminalPoints$to,
                            arrows = 'to',
                            FBgn = NA,
                            color = 'black',
                            width = 1,
                            symbol = NA,
                            fdr = NA,
                            GR = NA,
                            WT = NA,
                            title = '')

@@

@@

mean.cpm

@@

network.fun = function(comparison.T, comparison.M, cond1, cond2, pnp){
temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

visedges = purine.path
visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))

visedges$title = paste0(visedges$symbol,
                        "<br>FDR: ", visedges$fdr, 
                        "<br>",cond1," CPM: ", visedges$GR, 
                        "<br>",cond2," CPM: ", visedges$WT)
visedges = na.omit(visedges)
visedges = rbind(visedges, TerminalPoints)

node.names = unique(c(visedges$from, visedges$to))
node.data = data.frame(id = node.names,
                       color = 'dimgrey',
                       size = 10,
                       FC = NA,
                       pval = NA,
                       row.names = node.names)

@@

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
#node.data[names(node.colors),'size'] = 
#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
node.data[names(node.colors),'size'] = 
  (node.data[names(node.colors),'size'] + 4.5)*7.5

node.data[unique(TerminalPoints$enzyme), 'color'] = 'black'

node.data$group = 'metabolite'
node.data[node.data$color == 'black', 'group'] = "Outside Path"
node.data[node.data$color == 'dimgrey', 'group'] = "no data"

node.data$x = 1
node.data$y = 1
node.data["Excretion", 'x'] = -200
node.data["Excretion", 'y'] = 500

node.data["Pentose Phosphate" , 'x'] = 50
node.data["Pentose Phosphate" , 'y'] = -400

node.data["RNA.A", 'x'] = 850
node.data["RNA.A", 'y'] = -250

node.data["RNA.G", 'x'] = -1000
node.data["RNA.G", 'y'] = -250

node.data["Folate.Biosynthesis", 'x'] = -1000
node.data["Folate.Biosynthesis", 'y'] = -350

node.data["Riboflavin.Metabolism", 'x'] = -1000
node.data["Riboflavin.Metabolism", 'y'] = -150

node.data["DNA.A", 'x'] = 850
node.data["DNA.A", 'y'] = 250

node.data["DNA.G", 'x'] = -1000
node.data["DNA.G", 'y'] = 250

if(pnp == T){
  nodes[row.names(nodes) %in% colored.nodes, 'color'] = "lightgrey"
  visedges[row.names(visedges) %in% colored.edges, "color"] = 'lightgrey'
}

visNetwork(nodes,visedges,
                  main = paste0(cond1, " vs ", cond2))%>%
  visNodes(physics = T)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T, minVelocity = .5)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))%>%
    visLegend(addNodes = lnodes, useGroups = FALSE, width = .115)

>>>>

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')

mean.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)
cpmdata = G85R.cpm
groups = G85R.meta

@@

TerminalPoints = data.frame(enzyme = TerminalPoints$enzyme,
                            from = TerminalPoints$from,
                            to = TerminalPoints$to,
                            arrows = 'to',
                            FBgn = NA)

purine.path = rbind(purine.path, TerminalPoints)
row.names(purine.path) = 1:nrow(purine.path)
#write.csv(purine.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv")

@@

purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)

temp.edges = data.frame(from = purine.path$from,
                        to = purine.path$to,
                        arrows = purine.path$arrows,
                        color = "black",
                        width = 0,
                        title = "",
                        FBgn = purine.path$FBgn)

add.edges = data.frame(enzyme = c("3.5.4.10", 
                                "2.1.2.3",
                                "4.3.2.2",
                                "6.3.2.6",
                                "4.1.1.21",
                                "6.3.3.1",
                                "6.3.5.3",
                                "2.1.2.2",
                                "6.3.4.13",
                                "2.4.2.14",
                                "2.7.6.1"),
                       from = c("FAICAR", 
                                "AICA ribonucleotide", 
                                "SAICAR",
                                "CAIR",
                                "AIR",
                                "2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine",
                                "FGAR",
                                "GAR",
                                "Ribosylamine-5p",
                                "PRPP",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),

                       to = c("IMP", 
                              "FAICAR", 
                              "AICA ribonucleotide",
                              "SAICAR",
                              "CAIR",
                              "AIR",
                              "2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine",
                              "FGAR",
                              "GAR",
                              "Ribosylamine-5p",
                              "PRPP"),
                       arrows = c("to;from", 
                                  "to", 
                                  "to;from",
                                  "to;from",
                                  "to;from",
                                  "to",
                                  "to",
                                  "to",
                                  "to",
                                  "to",
                                  "to"),
                       FBgn = "")

#write.csv(temp.edges, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv")

i = 1
new.edges = data.frame(enzyme = as.character(),
                       from = as.character(),
                       to = as.character(),
                       arrows = as.character(),
                       FBgn = as.character())

while(i <= nrow(add.edges)){
  temp.fbgn = names(nodeID[grep(add.edges[i, "enzyme"], nodeID)])
  temp.fbgn = GeneIDKey[GeneIDKey$ensembl %in% temp.fbgn, "FBgn"]
  temp.new.edges = add.edges[rep(i, length(temp.fbgn)), ]
  temp.new.edges$FBgn = temp.fbgn
  new.edges = rbind(new.edges, temp.new.edges)
  i = i +1
}

purine.path = rbind(purine.path, new.edges)
row.names(purine.path) = 1:nrow(purine.path)
#write.csv(purine.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv")

temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)

new.edges$color = "black"
new.edges$width = 0
new.edges$title = ""

new.edges = new.edges[, colnames(temp.edges)]

temp.edges = rbind(temp.edges, new.edges)

#write.csv(temp.edges, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv")

@@

@@

temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)

purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)

temp.nodes = data.frame(id = unique(c(purine.path$from, purine.path$to)),
                        group = "metabolite",
                        color.background = "white",
                        color.border = "black",
                        x = 0,
                        y = 0,
                        size = 30,
                        FC = NA,
                        pval = NA,
                        title = "")
temp.nodes$title = temp.nodes$id

row.names(temp.nodes) = temp.nodes$id

temp.nodes[c("Pentose Phosphate", "Excretion", "Riboflavin.Metabolism",
            "Folate.Biosynthesis", "DNA.A", "DNA.G", "RNA.A", "RNA.G"), "group"] = "Outside Path"

temp.nodes["RNA.G", 'x'] = 0
temp.nodes["RNA.G", 'y'] = 1.5

temp.nodes["Folate.Biosynthesis", 'x'] = 0
temp.nodes["Folate.Biosynthesis", 'y'] = 2

temp.nodes["Riboflavin.Metabolism", 'x'] = 0
temp.nodes["Riboflavin.Metabolism", 'y'] = 2.5

temp.nodes["DNA.G", 'x'] = 0
temp.nodes["DNA.G", 'y'] = 4

temp.nodes["GTP", 'x'] = 1
temp.nodes["GTP", 'y'] = 2

temp.nodes["dGTP", 'x'] = 1
temp.nodes["dGTP", 'y'] = 4

temp.nodes["GDP", 'x'] = 2
temp.nodes["GDP", 'y'] = 3

temp.nodes["dGDP", 'x'] = 2
temp.nodes["dGDP", 'y'] = 3

temp.nodes["dGMP", 'x'] = 2
temp.nodes["dGMP", 'y'] = 4

temp.nodes["deoxyguanosine", 'x'] = 2
temp.nodes["deoxyguanosine", 'y'] = 5

temp.nodes["GMP", 'x'] = 3
temp.nodes["GMP", 'y'] = 2

temp.nodes["guanosine", 'x'] = 3
temp.nodes["guanosine", 'y'] = 3

temp.nodes["guanine", 'x'] = 3
temp.nodes["guanine", 'y'] = 4

temp.nodes["IDP", 'x'] = 4
temp.nodes["IDP", 'y'] = 1

temp.nodes["XMP", 'x'] = 4
temp.nodes["XMP", 'y'] = 2

temp.nodes["xanthosine", 'x'] = 4
temp.nodes["xanthosine", 'y'] = 3

temp.nodes["xanthine", 'x'] = 4
temp.nodes["xanthine", 'y'] = 4

temp.nodes["uric acid", 'x'] = 4
temp.nodes["uric acid", 'y'] = 5

temp.nodes["Excretion", 'x'] = 4
temp.nodes["Excretion", 'y'] = 6

temp.nodes = temp.nodes[temp.nodes$id != "Pentose Phosphate" ,]
temp.edges = temp.edges[temp.edges$from != "Pentose Phosphate" & temp.edges$to != "Pentose Phosphate" ,]

temp.nodes["FAICAR", "x"] = 5
temp.nodes["FAICAR", "y"] = 1

temp.nodes["AICA ribonucleotide", "x"] = 5
temp.nodes["AICA ribonucleotide", "y"] = 0

temp.nodes["IMP", 'x'] = 5
temp.nodes["IMP", 'y'] = 2

temp.nodes["inosine", 'x'] = 5
temp.nodes["inosine", 'y'] = 3

temp.nodes["hypoxanthine", 'x'] = 5
temp.nodes["hypoxanthine", 'y'] = 4

temp.nodes["deoxyinosine", 'x'] = 5
temp.nodes["deoxyinosine", 'y'] = 5

temp.nodes["adenylosuccinate", 'x'] = 6
temp.nodes["adenylosuccinate", 'y'] = 1

temp.nodes["AMP", 'x'] = 6
temp.nodes["AMP", 'y'] = 2

temp.nodes["adenosine", 'x'] = 6
temp.nodes["adenosine", 'y'] = 3

temp.nodes["adenine", 'x'] = 6
temp.nodes["adenine", 'y'] = 4

temp.nodes["deoxyadenosine", 'x'] = 6
temp.nodes["deoxyadenosine", 'y'] = 5

temp.nodes["cAMP", 'x'] = 7
temp.nodes["cAMP", 'y'] = 1

temp.nodes["ADP", 'x'] = 7
temp.nodes["ADP", 'y'] = 3

temp.nodes["dADP", 'x'] = 7
temp.nodes["dADP", 'y'] = 4

temp.nodes["dAMP", 'x'] = 7
temp.nodes["dAMP", 'y'] = 5

temp.nodes["ATP", 'x'] = 8
temp.nodes["ATP", 'y'] = 2

temp.nodes["dATP", 'x'] = 8
temp.nodes["dATP", 'y'] = 4

temp.nodes["RNA.A", 'x'] = 9
temp.nodes["RNA.A", 'y'] = 2

temp.nodes["DNA.A", 'x'] = 9
temp.nodes["DNA.A", 'y'] = 4

temp.nodes$x = temp.nodes$x*150
temp.nodes$y = temp.nodes$y*150

visNetwork(temp.nodes, temp.edges)%>%
  visNodes(physics = F)

#write.csv(temp.nodes, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv")

```{r}
temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)

temp.edges[temp.edges$from == "Pentose Phosphate", "to"] = "PRPP"

purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)

add.edges = data.frame(enzyme = c("2.2.1.1",
                                  "5.1.3.1",
                                  "5.3.1.6",
                                  "5.4.2.7",
                                  "5.4.2.2"),
                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
                       to = c("D-sedoheptulose-7-phosphate",
                              "D-Xylulose 5-phosphate",
                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
                       arrows = c("to;from",
                                  "to;from",
                                  "to;from",
                                  "to;from",
                                  "to;from"),
                       FBgn = "")

temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)

temp.edges[temp.edges$from == "Pentose Phosphate", "to"] = "PRPP"

purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)

temp.nodes = data.frame(id = unique(c(purine.path$from, purine.path$to)),
                        group = "metabolite",
                        color.background = "white",
                        color.border = "black",
                        x = 0,
                        y = 0,
                        size = 0,
                        FC = NA,
                        pval = NA,
                        title = "",
                        label = "")
temp.nodes$label = temp.nodes$id

row.names(temp.nodes) = temp.nodes$id

temp.nodes[c("Pentose Phosphate", "Excretion", "Riboflavin.Metabolism",
            "Folate.Biosynthesis", "DNA.A", "DNA.G", "RNA.A", "RNA.G"), "group"] = "Outside Path"

temp.nodes["Pentose Phosphate" , 'x'] = -2.5
temp.nodes["Pentose Phosphate" , 'y'] = -1.5

temp.nodes["D-ribose-1/5-phosphate / D-ribulose 5-phosphate", 'x'] = -3.5
temp.nodes["D-ribose-1/5-phosphate / D-ribulose 5-phosphate", 'y'] = 0.25

temp.nodes["PRPP", 'x'] = -2.5
temp.nodes["PRPP", 'y'] = 0

temp.nodes["Ribosylamine-5p", 'x'] = -1.5
temp.nodes["Ribosylamine-5p", 'y'] = 0.25

temp.nodes["GAR", 'x'] = -.5
temp.nodes["GAR", 'y'] = 0

temp.nodes["RNA.G", 'x'] = -.25
temp.nodes["RNA.G", 'y'] = 1

temp.nodes["Folate.Biosynthesis", 'x'] = -.25
temp.nodes["Folate.Biosynthesis", 'y'] = 1.5

temp.nodes["Riboflavin.Metabolism", 'x'] = -.25
temp.nodes["Riboflavin.Metabolism", 'y'] = 2

temp.nodes["DNA.G", 'x'] = 0
temp.nodes["DNA.G", 'y'] = 4.5

temp.nodes["FGAR", 'x'] = .5
temp.nodes["FGAR", 'y'] = 0.25

temp.nodes["GTP", 'x'] = .75
temp.nodes["GTP", 'y'] = 1.5

temp.nodes["dGTP", 'x'] = .75
temp.nodes["dGTP", 'y'] = 3.75

temp.nodes["2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine", 'x'] = 1.5
temp.nodes["2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine", 'y'] = 0

temp.nodes["GDP", 'x'] = 1.75
temp.nodes["GDP", 'y'] = 2.25

temp.nodes["dGDP", 'x'] = 1.5
temp.nodes["dGDP", 'y'] = 3

temp.nodes["dGMP", 'x'] = 1.75
temp.nodes["dGMP", 'y'] = 3.75

temp.nodes["AIR", 'x'] = 2.5
temp.nodes["AIR", 'y'] = 0.25

temp.nodes["deoxyguanosine", 'x'] = 2.75
temp.nodes["deoxyguanosine", 'y'] = 4.25

temp.nodes["GMP", 'x'] = 2.75
temp.nodes["GMP", 'y'] = 1.75

temp.nodes["CAIR", 'x'] = 3.5
temp.nodes["CAIR", 'y'] = 0

temp.nodes["guanosine", 'x'] = 3.5
temp.nodes["guanosine", 'y'] = 2.5

temp.nodes["guanine", 'x'] = 3.5
temp.nodes["guanine", 'y'] = 3.5

temp.nodes["IDP", 'x'] = 4.5
temp.nodes["IDP", 'y'] = 1.25

temp.nodes["SAICAR", 'x'] = 4.5
temp.nodes["SAICAR", 'y'] = 0.25

temp.nodes["XMP", 'x'] = 4.5
temp.nodes["XMP", 'y'] = 2

temp.nodes["xanthosine", 'x'] = 4.5
temp.nodes["xanthosine", 'y'] = 3

temp.nodes["xanthine", 'x'] = 4.5
temp.nodes["xanthine", 'y'] = 4

temp.nodes["uric acid", 'x'] = 4.5
temp.nodes["uric acid", 'y'] = 5

temp.nodes["Excretion", 'x'] = 4.5
temp.nodes["Excretion", 'y'] = 6

temp.nodes["AICA ribonucleotide", "x"] = 5.5
temp.nodes["AICA ribonucleotide", "y"] = 0

temp.nodes["FAICAR", "x"] = 5.5
temp.nodes["FAICAR", "y"] = 1

temp.nodes["IMP", 'x'] = 5.5
temp.nodes["IMP", 'y'] = 2

temp.nodes["inosine", 'x'] = 5.5
temp.nodes["inosine", 'y'] = 3

temp.nodes["hypoxanthine", 'x'] = 5.5
temp.nodes["hypoxanthine", 'y'] = 4

temp.nodes["deoxyinosine", 'x'] = 6.5
temp.nodes["deoxyinosine", 'y'] = 4.5

temp.nodes["adenylosuccinate", 'x'] = 6.5
temp.nodes["adenylosuccinate", 'y'] = 1.25

temp.nodes["AMP", 'x'] = 7.5
temp.nodes["AMP", 'y'] = 2

temp.nodes["adenosine", 'x'] = 6.5
temp.nodes["adenosine", 'y'] = 2.5

temp.nodes["adenine", 'x'] = 7.5
temp.nodes["adenine", 'y'] = 3

temp.nodes["deoxyadenosine", 'x'] = 7.5
temp.nodes["deoxyadenosine", 'y'] = 4

temp.nodes["cAMP", 'x'] = 8.25
temp.nodes["cAMP", 'y'] = 1.25

temp.nodes["ADP", 'x'] = 8.25
temp.nodes["ADP", 'y'] = 2.5

temp.nodes["dADP", 'x'] = 8.5
temp.nodes["dADP", 'y'] = 3

temp.nodes["dAMP", 'x'] = 8.5
temp.nodes["dAMP", 'y'] = 4

temp.nodes["ATP", 'x'] = 9
temp.nodes["ATP", 'y'] = 1.825

temp.nodes["dATP", 'x'] = 9.25
temp.nodes["dATP", 'y'] = 3.5

temp.nodes["RNA.A", 'x'] = 10
temp.nodes["RNA.A", 'y'] = 1.825

temp.nodes["DNA.A", 'x'] = 10
temp.nodes["DNA.A", 'y'] = 4

temp.nodes$x = temp.nodes$x*150
temp.nodes$y = temp.nodes$y*150

visNetwork(temp.nodes, temp.edges)%>%
  visNodes(physics = F, shape = "box")

#write.csv(temp.nodes, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv")

```{r}

##genes in the kegg pathway and their enzyme IDs
glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
##Edge data for genes connecting metabolites
glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
##Metabolites in the KEGG pathway with their ID
glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')

node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')

##extracting position data for nodes
node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
                       number = rep(names(node.data$kegg.names),
                                    lengths(node.data$kegg.names)),
                       x = 0,
                       y = 0,
                       color = 0,
                       names = "")
node.info$x = node.data$x[node.info$number]
node.info$y = node.data$y[node.info$number]

##make new columns for transcriptomic data
glycolysis.genes$FBgn = ""
glycolysis.genes$Symbol = ""
glycolysis.genes$FC = 0
glycolysis.genes$pval = 1

##Isolate gene ID info for goi
temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
row.names(temp) = temp$CG

##fill in new columns with transcriptomic data
glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
glycolysis.genes$FC = 0
glycolysis.genes$FC = 0

##make new columns for metabolomic data
row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
glycolysis.metabs$metabolomicsID = ""
glycolysis.metabs$FC = 0
glycolysis.metabs$pval = 1

##retrieve name used in metabolomic data for metabolite IDs in path
##including IDs associated with multiple metabolomic names
i = 1
while(i<=nrow(glycolysis.metabs)){
  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
  }
  i = i +1
}

##retrieve metabolite fold change and pvalue data
glycolysis.metabs$FC = 0
glycolysis.metabs$pval = 0

##using the positions for nodes (metabolites) only
metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]

metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']

color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)

metab.info$color[metab.info$color > 1] = 1
metab.info$color[metab.info$color < -1] = -1
metab.info$color = (metab.info$color * 200) +201
metab.info$color = color.pallette[metab.info$color]
metab.info$color[is.na(metab.info$color)] = 'dimgrey'

metab.info$size = 10 + 10*abs(metab.info$size)
metab.info$size[is.na(metab.info$size)] = 10

metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
                          "<br>log2(FC): ", signif(metab.info$FC,3),
                          "<br>pval: ", signif(10^-metab.info$pval,3))

nodes = data.frame(id = paste0(metab.info$names),
                   color = metab.info$color,
                   size = metab.info$size,
                   x = 2*metab.info$x,
                   y = 2*metab.info$y,
                   physics = F,
                   group = "",
                   title = metab.info$title)

glycolysis.edges$FBgn = ''
temp.glycolysis.path = glycolysis.edges

i = 1
while(i<=nrow(glycolysis.edges)){
  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
    temp2 = glycolysis.edges[rep(i, length(temp)),]
    temp2$FBgn = temp
  }else{
    temp2 = glycolysis.edges[i,]
  }
  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)

  i = i +1
}

glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]

glycolysis.edges$size = 0
glycolysis.edges$size[glycolysis.edges$size <1] = 1
glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
glycolysis.edges$size = 2*glycolysis.edges$size

glycolysis.edges$color = "white"
## max color intensity is at FC of 2
#glycolysis.edges$color[glycolysis.edges$color>2] = 2
#glycolysis.edges$color[glycolysis.edges$color<(-2)] = -2
#glycolysis.edges$color = 201+(glycolysis.edges$color *100)
#glycolysis.edges$color = color.pallette[glycolysis.edges$color]
#glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))

glycolysis.edges = data.frame(from = glycolysis.edges$from.name,
                              to = glycolysis.edges$to.name)
,
                              arrows = glycolysis.edges$arrow)
,
                              color = glycolysis.edges$color)
,
                              width = glycolysis.edges$size)
,
                              title = glycolysis.edges$title,
                              physics = T)

nodes = data.frame(id = paste0(nodes$id),
                   color = nodes$color,
                   size = nodes$size,
                   x = nodes$x,
                   y = nodes$y,
                   physics = F,
                   group = "",
                   title = nodes$title)

OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
                               'Propanoate Metabolism',
                               'Starch and Sucrose Metabolism',
                               'Citrate Cycle'),
                        color = "black",
                        size = 15,
                        x= c(1350,1254,966,175),
                        y=c(1112,1822,110,1700),
                        physics = F,
                        group = 'Outside Path',
                        title = "")

nodes = rbind(nodes, OutsidePath)

network.fun = function(comparison.T, comparison.M, cond1, cond2, pnp){
temp = colorRampPalette(c("dodgerblue", 'royalblue', "firebrick",'red'))(401)

visedges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))
visedges$title = paste0(visedges$symbol,
                        "<br>FDR: ", visedges$fdr, 
                        "<br>",cond1," CPM: ", visedges$GR, 
                        "<br>",cond2," CPM: ", visedges$WT)

@@

node.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv", row.names = 1)
node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
node.data[,'size'] = (node.data[,'size'] + 4.5)*7.5
node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2
node.colors = (node.colors*100)+201
node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color.background'] = node.colors
node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)
node.data[node.data$group == "Outside Path", 'color.background'] = 'black'
node.data[node.data$color.background == 'white', 'group'] = "no data"

nodes = node.data
nodes[names(node.pval[node.pval > 0.05]), "color"] = 'grey'

visedges$color[visedges$from %in% row.names(nodes)[nodes$group == "Outside Path"]] = 'black'
visedges$color[visedges$to %in% row.names(nodes)[nodes$group == "Outside Path"]] = 'black'
visedges = visedges[,c('from', 'to', 'arrows', 'color', 'width', 'title')]
row.names(visedges) = c(1:nrow(visedges))
visedges = visedges[!is.na(visedges$color),]

lnodes <- data.frame(label = c("Sig. Increased", "Sig. Decreased", "Not. Sig.", "No Data"), 
shape = 'dot', color = list(background = c("red", "dodgerblue",'dimgrey', 'white'), border = "black"),
size = c(40, 15, 25, 25),
 title = "")

visNetwork(nodes,visedges,
                  main = paste0(cond1, " vs ", cond2))%>%
  visNodes(physics = F)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))%>%
    visLegend(addNodes = lnodes, useGroups = FALSE, width = .115)
